Sparse spectral and $p$-finite element methods on disk-slices and rhombi I: zero boundary conditions

### 2019-02-19 papers/halfdisk/halfdisk.tex
First draft of poster for HD. Minor edits to paper.
Further edits to paper

\newcommand{\Pnk}{P_{n,k}}
\newcommand{\Pnkab}{P_{n,k}^{(a,b)}}
\newcommand{\Wab}{{W^{(a,b)}}}
\newcommand{\Pmjab}{P_{m,j}^{(a,b)}}
\newcommand{\alphaab}{\alpha^{(a,b)}}
\newcommand{\betaab}{\beta^{(a,b)}}
\newcommand{\bigPab}{\bigP^{(a,b)}}
\newcommand{\Dnt}{D^T_n}
\newcommand{\Wii}{W^{(1,1)}}
\newcommand{\Pii}{P^{(1,1)}}
\newcommand{\bigPii}{{\mathbb{P}^{(1,1)}}}
\newcommand{\Poo}{P^{(0,0)}}
\newcommand{\bigPoo}{{\mathbb{P}^{(0,0)}}}
\newcommand{\Poi}{P^{(0,1)}}
\newcommand{\Pio}{P^{(1,0)}}
\newcommand{\dx}{\frac{\partial}{\partial x}}
\newcommand{\dy}{\frac{\partial}{\partial y}}
\newcommand{\element}{\tau}
\newcommand{\refelement}{\hat{\tau}}
\newcommand{\FEset}{\mathcal{T}}
\newcommand{\bigW}{\mathbb{W}}
\newcommand{\bigWii}{{\mathbb{W}^{(1,1)}}}

@@

For the half disk, the weight $W^{(a,b)}(x,y)$ results from setting:

@@

Three-term recurrences lead to Jacobi operators that correspond to multiplication by $x$ and $y$. Set \(J_x^{(a,b)}, J_y^{(a,b)}\) as the \(\half (N+1)(N+2) \times \half (N+1)(N+2)\) Jacobi matrices corresponding to
\begin{align}
J_x^{(a,b)} \bigPab(x,y) = x \bigPab(x,y), \quad J_y^{(a,b)} \bigPab(x,y) = y \bigPab(x,y).
\end{align}
Then  \(J_x^{(a,b)}, J_y^{(a,b)}\) have the Banded-Block-Banded structures
\begin{align}
J_{x/y}^{(a,b)} &= \begin{bmatrix}
		B^{x/y}_0 & A^{x/y}_0 & & & & \\
		C^{x/y}_1 & B^{x/y}_1 & A^{x/y}_1 & & & \\
		& C^{x/y}_2 & B^{x/y}_2 & A^{x/y}_2  & & & \\
		& & C^{x/y}_3 & \ddots & \ddots & \\
		& & & \ddots & \ddots & \ddots \\
	\end{bmatrix}
\end{align}
where
\begin{align}
A^x_n &:= \begin{bmatrix}
		\alphaab_{n+1,0,1} & 0 & \hdots & 0 \\
		& \ddots & & \vdots & \\
		& & \alphaab_{n+1,n,1} & 0 \\
	    \end{bmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots,N-1 \\
B^x_n &:= \begin{bmatrix}
		\alphaab_{n,0,2} & & \\
		& \ddots & \\
		& & \alphaab_{n,n,2} \\
	    \end{bmatrix} \in \R^{(n+1)\times(n+1)} \quad n = 0,1,2,\dots,N \\
C^x_n &:= \big( A^x_n \big)^T \in \R^{(n+1)\times n},  \quad n = 1,2,\dots,N, \\ 
\nonumber \\
A^y_n &:= \begin{bmatrix}
		0 & \betaab_{n,0,6} & & & \\
		\betaab_{n,1,5} & 0 & & & \\
		& \ddots & \ddots & \ddots & \\
		& & \betaab_{n,n,5}& 0 & \betaab_{n,n,6} \\
	    \end{bmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots,N-1 \\
B^y_n &:= \begin{bmatrix}
		0 & \betaab_{n,0,4} & & \\
		\betaab_{n,1,3} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-1,4} \\
		& & \betaab_{n,n,3} & 0
	    \end{bmatrix} \in \R^{(n+1)\times(n+1)}  \quad n = 0,1,2,\dots,N \\
C^y_n &:= \begin{bmatrix}
		0 & \betaab_{n,0,2} & & \\
		\betaab_{n,1,1} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-2,2} \\
		& & \ddots & 0 \\
		& & & \betaab_{n,n,1} \\
	    \end{bmatrix} \in \R^{(n+1)\times n}, \quad n = 1,2,\dots,N.
\end{align}

@@

For general \(a,b\) and general functions \(f(x,y) = \bigPab(x,y)^\top \mathbf{f}\), there exist sparse operators \(D_x^{(a,b)}, \: D_y^{(a,b)}, \: W_x^{(a,b)}, \: W_y^{(a,b)}\) such that:
\begin{align}
\dx[f(x,y)] &= \bigP^{(a+1,b+1)}(x,y)^T \: D_x^{(a,b)} \: \mathbf{f}, \\
\dy[f(x,y)] &= \bigP^{(a,b+1)}(x,y)^T \: D_y^{(a,b)} \: \mathbf{f}, \\
\dx[\Wab(x,y) \: f(x,y)] &= W^{(a-1,b-1)}(x,y) \: \bigP^{(a-1,b-1)}(x,y)^T \: W_x^{(a,b)} \: \mathbf{f}, \\
\dy[\Wab(x,y) \: f(x,y)] &= W^{(a,b-1)}(x,y) \: \bigP^{(a,b-1)}(x,y)^T \: W_y^{(a,b)} \: \mathbf{f}.
\end{align}
The incrementing and decrementing of parameters as seen here is analogous to other well known orthogonal polynomials families' derivatives, for example the Jacobi polynomials, as seen in the DLMF \cite{DLMFDerivatives}.
Further, we note that there exist Banded-Block-Banded matrix operators \(T^{(1,0)\to(0,0)}\), \(T^{(0,1)\to(1,1)}\) and $T^{(0,2)\to(2,2)}$ such that:
\begin{align}
x \bigP^{(1,0)}(x,y) &= \Big(T^{(1,0)\to(0,0)} \Big)^T \: \bigP^{(0,0)}(x,y) \\
\bigP^{(0,1)}(x,y) &= \Big(T^{(0,1)\to(1,1)} \Big)^T \: \bigP^{(1,1)}(x,y) \\
\bigP^{(0,2)}(x,y) &= \Big(T^{(0,2)\to(2,2)} \Big)^T \: \bigP^{(2,2)}(x,y)
\end{align}

We can then obtain the matrix operator for \(\Delta\), that will take us from coefficients for expansion in the weighted space
\[
\Wii(x,y) \: \bigPii(x,y)
\]
to coefficients in the non-weighted space
\[
\bigPii(x,y).
\]
Importantly, this operator will have Banded-Block-Banded structure, and hence will be sparse. Note that this construction will ensure the imposition of the Dirichlet zero boundary conditions on $\Omega$. The matrix operator \(\Delta\) acting on the coefficients vector is then given by
\begin{align}
    \Delta := D_x^{(0,0)} \: W_x^{(1,1)} + T^{(0,1)\to(1,1)} \: D_y^{(0,0)} \: T^{(1,0)\to(0,0)} \: W_y^{(1,1)}.
\end{align}

@@

@@

%
\section{P-finite element methods using sparse operators}

@@

Fix \(a, b = 1,1\). Find \(u(x,y)\) given a function \(f(x,y)\) such that:
\begin{align}
    \Delta(\Wii \: u)(x,y) = f(x,y) \quad \text{in } \Omega
\end{align}
    where we recall
\begin{align}
    \Wii(x,y) = x \: (1-x^2-y^2)
\end{align}
which ensures a boundary condition that \((\Wii \: u)(x,y) = 0\) on \(\partial \Omega\).

The first step is to obtain the expansion of \(f\) in the \(\Pii\) basis, i.e. obtain the vector \(\mathbf{f}\) such that \(f(x,y) = \mathbf{f}^T \: \bigP^{(1,1)}(x,y) = \sum_{n=0}^N \mathbf{f}_n^T \: \bigP_n^{(1,1)}(x,y)\) for some \(N \in \N\). The coefficients of \(u\) in the \(\Pii\) basis are then given by 
\begin{align}
    \mathbf{u} = \Delta \text{\textbackslash} \mathbf{f}.
\end{align}

\begin{figure}
	\includegraphics[scale=0.4]{example4coeffs}
\centering
\caption{Plot of the difference between the previous solution's coefficients and the current solution's coefficients under increasing degree of approximation (number of coefficients used) for $N = 2,\dots,10$, using RHS of $f(x,y) = 2(1-x^2-y^2)\cos(x) - 8x\sin(x) - x(1-x^2-y^2)\sin(x) - 4x^2 \cos(x) - 12xy$ for the Poisson equation. The solution is converging as seen by the decreasing (absolute value) difference of coefficient values.}
\centering
\label{fig:poisson}
\end{figure}

Fix \(a, b = 1,1\). Find \(u(x,y)\) given a function \(f(x,y)\) such that:
\begin{align}
    \Delta(\Wii u)(x,y) + k^2 u(x,y) = - f(x,y) \quad \text{in } \Omega
\end{align}
noting that this ensures a boundary condition that \((\Wii \: u)(x,y) = 0\) on \(\partial \Omega\).

Again, the first step is to obtain the expansion of \(f\) in the \(\Pii\) basis. The coefficients of \(u\) in the \(\Pii\) basis are then given by 
\begin{align}
    \mathbf{u} = - (k^2I + \Delta) \text{\textbackslash} \mathbf{f}.
\end{align}

\subsection{Heat Equation}
Fix \(a, b = 1,1\), and consider
\begin{align}
\frac{\partial u}{\partial t}(x,y) = \Delta(\Wii \: u)(x,y) \quad \text{in } \Omega
\end{align}

Using a backward Euler time-stepping method, we can formulate this for \(t = 0,1,2,\dots\) and step length $h$:
\begin{align}
u_{t+1}(x,y) - u_t (x,y) = h \Delta(\Wii \: u_{t+1})(x,y) \quad \text{for } (x,y) \in \Omega.
\end{align}

There exist $N \in \N$ such that, for each $t = 0,1,2,\dots$, $u_t (x,y) = \sum_{n=0}^N \mathbf{u_t}_n^T \: \bigP_n^{(1,1)}(x,y) = \mathbf{u}_t^T \; \bigP^{(1,1)}(x,y)$. Then, using the operator $\Delta$, we can solve this system for a given initial condition $\mathbf{u_0}$ by iterating for $t = 0,1,2,\dots,t_{max}$:
\begin{align}
    \mathbf{u_{t+1}} &= (I - h \Delta) \: \text{\textbackslash} \: \mathbf{u_t}, \\
    \big( u_{t+1}(x,y) &= \mathbf{u}_{t+1}^T \; \bigP^{(1,1)}(x,y) \big) \nonumber.
\end{align}

\begin{figure}
	\includegraphics[scale=0.4]{example2timesteppingcovnvergence}
\centering
\caption{Plot of the current iteration's coefficients for the heat equation example, using degree of approximation $N = 5$ with initial condition of $u_0(x,y) = \Wii(x,y)$ and step size $h=0.01$, plotted for iterations $t=100, 120, \dots, 200$. The solution tends to zero, as seen by the decreasing (absolute value) coefficient values.}
\centering
\label{fig:heateqn}
\end{figure}

>>>>

\newcommand{\Pnk}{P_{n,k}}
\newcommand{\Pnkab}{P_{n,k}^{(a,b)}}
\newcommand{\Wab}{{W^{(a,b)}}}
\newcommand{\Pmjab}{P_{m,j}^{(a,b)}}
\newcommand{\alphaab}{\alpha^{(a,b)}}
\newcommand{\betaab}{\beta^{(a,b)}}
\newcommand{\bigPab}{\bigP^{(a,b)}}
\newcommand{\Dnt}{D^T_n}
\newcommand{\Wii}{W^{(1,1)}}
\newcommand{\Pii}{P^{(1,1)}}
\newcommand{\bigPii}{{\mathbb{P}^{(1,1)}}}
\newcommand{\Poo}{P^{(0,0)}}
\newcommand{\bigPoo}{{\mathbb{P}^{(0,0)}}}
\newcommand{\Poi}{P^{(0,1)}}
\newcommand{\Pio}{P^{(1,0)}}
\newcommand{\dx}{\frac{\partial}{\partial x}}
\newcommand{\dy}{\frac{\partial}{\partial y}}
\newcommand{\element}{\tau}
\newcommand{\refelement}{\hat{\tau}}
\newcommand{\FEset}{\mathcal{T}}
\newcommand{\bigW}{\mathbb{W}}
\newcommand{\bigWab}{\mathbb{W}^{(a,b)}}
\newcommand{\bigWii}{{\mathbb{W}^{(1,1)}}}

@@

For the half disk, the weight $W^{(a,b)}(x,y) = x^a \: (1-x^2-y^2)^b$ results from setting:

@@

Three-term recurrences lead to Jacobi operators that correspond to multiplication by $x$ and $y$. Define, for some $N \in \No$:
\begin{align}
\bigPab_n := \begin{bmatrix}
		P^{(a,b)}_{n,-n}(x,y) \\
		\vdots \\
		P^{(a,b)}_{n,n}(x,y)
	\end{bmatrix} \in \R^{n+1}, 
\quad \quad 
\bigPab := \begin{bmatrix}
		\bigPab_0 \\
		\bigPab_1 \\
		\vdots \\
		\bigPab_N
	\end{bmatrix}
\end{align}
and set \(J_x^{(a,b)}, J_y^{(a,b)}\) as the \(\half (N+1)(N+2) \times \half (N+1)(N+2)\) Jacobi matrices corresponding to
\begin{align}
J_x^{(a,b)} \bigPab(x,y) = x \bigPab(x,y), \quad J_y^{(a,b)} \bigPab(x,y) = y \bigPab(x,y).
\end{align}
Then  \(J_x^{(a,b)}, J_y^{(a,b)}\) have the Banded-Block-Banded structures
\begin{align}
J_{x/y}^{(a,b)} &= \begin{bmatrix}
		B^{x/y}_0 & A^{x/y}_0 & & & & \\
		C^{x/y}_1 & B^{x/y}_1 & A^{x/y}_1 & & & \\
		& C^{x/y}_2 & B^{x/y}_2 & A^{x/y}_2  & & & \\
		& & C^{x/y}_3 & \ddots & \ddots & \\
		& & & \ddots & \ddots & \ddots \\
	\end{bmatrix}
\end{align}
where
\begin{align}
A^x_n &:= \begin{bmatrix}
		\alphaab_{n+1,0,1} & 0 & \hdots & 0 \\
		& \ddots & & \vdots & \\
		& & \alphaab_{n+1,n,1} & 0 \\
	    \end{bmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots,N-1 \\
B^x_n &:= \begin{bmatrix}
		\alphaab_{n,0,2} & & \\
		& \ddots & \\
		& & \alphaab_{n,n,2} \\
	    \end{bmatrix} \in \R^{(n+1)\times(n+1)} \quad n = 0,1,2,\dots,N \\
C^x_n &:= \big( A^x_n \big)^T \in \R^{(n+1)\times n},  \quad n = 1,2,\dots,N, \\ 
\nonumber \\
A^y_n &:= \begin{bmatrix}
		0 & \betaab_{n,0,6} & & & \\
		\betaab_{n,1,5} & 0 & & & \\
		& \ddots & \ddots & \ddots & \\
		& & \betaab_{n,n,5}& 0 & \betaab_{n,n,6} \\
	    \end{bmatrix} \in \R^{(n+1)\times(n+2)}, \quad n = 0,1,2,\dots,N-1 \\
B^y_n &:= \begin{bmatrix}
		0 & \betaab_{n,0,4} & & \\
		\betaab_{n,1,3} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-1,4} \\
		& & \betaab_{n,n,3} & 0
	    \end{bmatrix} \in \R^{(n+1)\times(n+1)}  \quad n = 0,1,2,\dots,N \\
C^y_n &:= \begin{bmatrix}
		0 & \betaab_{n,0,2} & & \\
		\betaab_{n,1,1} & 0 & \ddots & \\
		& \ddots & \ddots & \betaab_{n,n-2,2} \\
		& & \ddots & 0 \\
		& & & \betaab_{n,n,1} \\
	    \end{bmatrix} \in \R^{(n+1)\times n}, \quad n = 1,2,\dots,N.
\end{align}

@@

Firstly, we introduce further notation that
\begin{align}
\bigWab(x,y) := \Wab(x,y) \bigPab(x,y).
\end{align}

For general \(a,b\) and general functions \(f(x,y) = \bigPab(x,y)^\top \mathbf{f}\), there exist sparse operators \(D_x^{(a,b)}, \: D_y^{(a,b)}, \: W_x^{(a,b)}, \: W_y^{(a,b)}\) such that:
\begin{align}
\dx[f(x,y)] &= \bigP^{(a+1,b+1)}(x,y)^T \: D_x^{(a,b)} \: \mathbf{f}, \\
\dy[f(x,y)] &= \bigP^{(a,b+1)}(x,y)^T \: D_y^{(a,b)} \: \mathbf{f}, \\
\dx[\Wab(x,y) \: f(x,y)] &= \bigW^{(a-1,b-1)}(x,y)^T \: W_x^{(a,b)} \: \mathbf{f}, \\
\dy[\Wab(x,y) \: f(x,y)] &= \bigW^{(a,b-1)}(x,y)^T \: W_y^{(a,b)} \: \mathbf{f}.
\end{align}
The incrementing and decrementing of parameters as seen here is analogous to other well known orthogonal polynomials families' derivatives, for example the Jacobi polynomials, as seen in the DLMF \cite{DLMFDerivatives}.

Further, we note that there exist "parameter transformation" Banded-Block-Banded matrix operators that increment/decrement the parameters, transforming the OPs from one (weighted or non-weighted) parameter space to another. We denote these operators as $T_W^{(1,0)\to(0,0)}$, $T_W^{(1,1)\to(0,0)}$, $T^{(0,1)\to(1,1)}$, $T^{(0,2)\to(2,2)}$ and the general $T^{(a,b)\to(a+1,b+1)}$ where:
\begin{align}
\bigW^{(1,0)}(x,y) &= \Big(T_W^{(1,0)\to(0,0)} \Big)^T \: \bigP^{(0,0)}(x,y) \\
\bigW^{(1,1)}(x,y) &= \Big(T_W^{(1,1)\to(0,0)} \Big)^T \: \bigP^{(0,0)}(x,y) \\
\bigP^{(0,1)}(x,y) &= \Big(T^{(0,1)\to(1,1)} \Big)^T \: \bigP^{(1,1)}(x,y) \\
\bigP^{(0,2)}(x,y) &= \Big(T^{(0,2)\to(2,2)} \Big)^T \: \bigP^{(2,2)}(x,y) \\
\bigP^{(a,b)}(x,y) &= \Big(T^{(a,b)\to(a+1,b+1)} \Big)^T \: \bigP^{(a+1,b+1)}(x,y)
\end{align}

We can then obtain the matrix operator for \(\Delta\), that will take us from coefficients for expansion in the weighted space
\[
\bigWii(x,y) = \Wii(x,y) \: \bigPii(x,y)
\]
to coefficients in the non-weighted space
\[
\bigPii(x,y).
\]
Importantly, this operator will have Banded-Block-Banded structure, and hence will be sparse. Note that this construction will ensure the imposition of the Dirichlet zero boundary conditions on $\Omega$. The matrix operator \(\Delta\) acting on the coefficients vector is then given by
\begin{align}
    \Delta := D_x^{(0,0)} \: W_x^{(1,1)} + T^{(0,1)\to(1,1)} \: D_y^{(0,0)} \: T_W^{(1,0)\to(0,0)} \: W_y^{(1,1)}.
\end{align}

@@

????

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.4]{solutionblocknorms}
	\caption{The norms of each block of the computed solution of the Poisson equation with the given right hand side functions.}
	\centering
	\label{fig:solutionblocknorms}
\end{figure}

Find \(u(x,y)\) given a function \(f(x,y)\) such that:
\begin{align}
	\begin{cases}
    		\Delta u(x,y) = f(x,y) \quad \text{in } \Omega \\
		u(x,y) = 0 \quad \text{on } \partial \Omega
	\end{cases}.
\end{align}
noting the imposition of zero Dirichlet boundary conditions on $u$.

We can tackle the problem as follows. Fix \(a, b = 1,1\). Denote the coefficient vector for expansion of $u$ in the $\bigWii$ OP basis up to degree $N$ by $\mathbf{u}$, and the coefficient vector for expansion of $f$ in the $\bigPii$ OP basis up to degree $N$ by $\mathbf{f}$. Since $f$ is known, we can obtain $\mathbf{f}$ using the quadrature rule above. In matrix-vector notation, our system hence becomes:
\begin{align}
    \Delta^{(1,1)} \mathbf{u} = \mathbf{f}
\end{align}
which can be solved to find $\mathbf{u}$.

%\begin{figure}
%	\includegraphics[scale=0.4]{example4coeffs}
%\centering
%\caption{Plot of the difference between the previous solution's coefficients and the current solution's coefficients under increasing degree of approximation (number of coefficients used) for $N = 2,\dots,10$, using RHS of $f(x,y) = 2(1-x^2-y^2)\cos(x) - 8x\sin(x) - x(1-x^2-y^2)\sin(x) - 4x^2 \cos(x) - 12xy$ for the Poisson equation. The solution is converging as seen by the decreasing (absolute value) difference of coefficient values.}
%\centering
%\label{fig:poisson}
%\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.4]{sparsityoflaplacian}
        \label{fig:sparsity}
    	\caption{A "spy" plot of the $\Delta$ operator for $\bigWii(x,y) \to \bigPii(x,y)$ showing its sparsity.}
	\centering
\end{figure}

Find \(u(x,y)\) given a function \(f(x,y)\) such that:
\begin{align}
	\begin{cases}
    		\Delta u(x,y) + k^2 u(x,y) = f(x,y) \quad \text{in } \Omega \\
		u(x,y) = 0 \quad \text{on } \partial \Omega
	\end{cases}.
\end{align}
noting the imposition of zero Dirichlet boundary conditions on $u$.

We can tackle the problem as follows. Fix \(a, b = 1,1\). Denote the coefficient vector for expansion of $u$ in the $\bigWii$ OP basis up to degree $N$ by $\mathbf{u}$, and the coefficient vector for expansion of $f$ in the $\bigPii$ OP basis up to degree $N$ by $\mathbf{f}$. Since $f$ is known, we can obtain $\mathbf{f}$ using the quadrature rule above. In matrix-vector notation, our system hence becomes:
\begin{align}
    (\Delta^{(1,1)} + k^2 T^{(0,0)\to(1,1)} T_W^{(1,1)\to(0,0)}) \mathbf{u} = \mathbf{f}
\end{align}
which can be solved to find $\mathbf{u}$.

We can extend this to constant non-zero boundary conditions by simply noting that the problem 
\begin{align}
	\begin{cases}
    		\Delta u(x,y) + k^2 u(x,y) = f(x,y) \quad \text{in } \Omega \\
		u(x,y) = c \in \R \quad \text{on } \partial \Omega
	\end{cases}
\end{align}
is equivalent to letting $u = v + c$ and solving
\begin{align}
	\begin{cases}
    		\Delta v(x,y) + k^2 v(x,y) = f(x,y) - k^2 c =: g(x,y)  \quad \text{in } \Omega \\
		v(x,y) = 0 \quad \text{on } \partial \Omega
	\end{cases}.
\end{align}

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{solution}
        	\label{fig:solution}
    	\caption{The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$.}
	\centering
\end{figure}

\subsection{Heat Equation}
Consider
\begin{align}
	\begin{cases}
		\frac{\partial u}{\partial t}(t,x,y) = \Delta u(t,x,y) \quad \text{in } \Omega \\
		u(t, x, y) = 0 \quad \text{on } \partial \Omega \\
		u(0, x, y) = u_0(x,y) := \Wii(x,y) \: f(x,y)
	\end{cases}
\end{align}
noting the imposition of zero Dirichlet boundary conditions.

Using a backward Euler time-stepping method, we can formulate this for \(t = 0,1,2,\dots\) and step length $h$:
\begin{align}
u_{t+1}(x,y) - u_t (x,y) = h \: \Delta u_{t+1}(x,y) \quad \text{for } (x,y) \in \Omega.
\end{align}

We can tackle the problem as follows. Fix \(a, b = 1,1\). Denote the coefficient vector for expansion of $u_0$ in the $\bigWii$ OP basis up to degree $N$ by $\mathbf{u}_0$, and similarly for each $t = 1,2,3,\dots,t_{max}$ we denote $\mathbf{u}_t$ as the coefficient vector of the expansion of $u_t$ in the $\bigWii$ OP basis up to degree $N$. Further, denote the coefficient vector for expansion of $u_0$ in the $\bigPii$ OP basis up to degree $N$ by $\mathbf{\tilde{u}}_0$, and similarly for each $t = 1,2,3,\dots,t_{max}$ denote $\mathbf{\tilde{u}}_t$ as the coefficient vector of the expansion of $u_t$ in the $\bigPii$ OP basis up to degree $N$.

Then, using the operator $\Delta$, we can solve this system for the given initial condition $\mathbf{u_0}$ by iterating for $t = 0,1,2,\dots,t_{max}$:
\begin{align}
	&T^{(0,0)\to(1,1)} \: T_W^{(1,1)\to(0,0)} \: (\mathbf{u}_{t+1} - \mathbf{u}_t) = h \: \Delta^{(1,1)} \mathbf{u}_{t+1} \nonumber \\
	\iff& (T^{(0,0)\to(1,1)} \:T_W^{(1,1)\to(0,0)} - h \: \Delta^{(1,1)}) \: \mathbf{u}_{t+1} = T^{(0,0)\to(1,1)} \: T_W^{(1,1)\to(0,0)} \: \mathbf{u}_t \nonumber \\
	\iff& \mathbf{u}_{t+1} = (T^{(0,0)\to(1,1)} \: T_W^{(1,1)\to(0,0)} - h \: \Delta^{(1,1)})^{-1} T^{(0,0)\to(1,1)} \: T_W^{(1,1)\to(0,0)} \: \mathbf{u}_t \nonumber \\
	\iff& \mathbf{\tilde{u}}_{t+1} = T^{(0,0)\to(1,1)} \: T_W^{(1,1)\to(0,0)} \: (T^{(0,0)\to(1,1)} \: T_W^{(1,1)\to(0,0)} - h \: \Delta^{(1,1)})^{-1} \: \mathbf{\tilde{u}}_t.
\end{align}

%\begin{figure}
%	\includegraphics[scale=0.4]{example2timesteppingcovnvergence}
%\centering
%\caption{Plot of the current iteration's coefficients for the heat equation example, using degree of approximation $N = 5$ with initial condition of $u_0(x,y) = \Wii(x,y)$ and step size $h=0.01$, plotted for iterations $t=100, 120, \dots, 200$. The solution tends to zero, as seen by the decreasing (absolute value) coefficient values.}
%\centering
%\label{fig:heateqn}
%\end{figure}

%
\appendix
%
\section{P-finite element methods using sparse operators}

@@

\section{Disk Slices}

The work in this paper on the half disk can be easily transferred to the domain of a disk slice by which we mean
\begin{align}
	\Omega := \{(x,y) \in \R^2 \quad | \quad \alpha < x < \beta, \: \gamma \rho(x) < y < \delta \rho(x)\}
\end{align}
with $\alpha, \beta \in [0,1]$, $\rho(x) = \sqrt{1-x^2}$, and  $-\gamma = \delta  = $
